Using Fundamental Measure Theory to treat the Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-08-22 papers/pair-correlation/paper.tex
add triplet plots to paper, fix triplet plot title, and make it build without necessary triplet MC data Tested everything on darcy.

>>>>

\subsection{Triplet distribution function}

In Fig.~\ref{fig:triplet-distribution-3} and
Fig.~\ref{fig:triplet-distribution-4} we can see the triplet
distribution computed using Monte Carlo.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-alt-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    in contact.}\label{fig:triplet-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-alt-4.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:triplet-distribution-4}
\end{figure}
